New perspectives on multiplicative functions: Lambda-rings and Tannakian symbols

### 2018-04-27 sections/10-algebraicgeometry.tex

Recall that an element $x$ of a ring $R$ is called \defhl{invertible} if there exists an element $y$ in $R$ such that $xy = 1$. Recall also that there is a functor from commutative rings to sets which sends a ring to its subset of invertible elements. This functor is usually denoted by $\mathbb{G}_m$ and it is an example of what in algebraic geometry is called a \emph{scheme}. If $R$ is any commutative ring, we write $\mathbb{G}_m(R)$ for the set of invertible elements in $R$. Restating the above two observations in equations, we see that
$$  \varphi(p^e) = \# \mathbb{G}_m(\Z / p^e)  $$
and 
$$  \varphi'(p^e) = \# \mathbb{G}_m(\mathbb{F}_{p^e})  $$
Recall that we use the hashtag symbol $\#$ as shorthand for ``the number of elements in the set \ldots''.

>>>>

Recall that an element $x$ of a ring $R$ is called \defhl{invertible} if there exists an element $y$ in $R$ such that $xy = 1$. Recall also that there is a functor from commutative rings to sets which sends a ring to its subset of invertible elements. This functor is usually denoted by $\mathbb{G}_m$ and it is an example of what in algebraic geometry is called a \emph{scheme}. If $R$ is any commutative ring, we write $\mathbb{G}_m(R)$ for the set of invertible elements in $R$. Restating the above two observations in equations, we see that
$$  \varphi(p^e) = \# \mathbb{G}_m(\Z / p^e)  $$
and 
$$  \varphi'(p^e) = \# \mathbb{G}_m(\mathbb{F}_{p^e})  $$
Recall that we use the number sign $\#$ as shorthand for ``the number of elements in the set \ldots''.
